---
title: "Alcohol vs Seat choice"
author: "Estrella Aguilar"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
    
 We see in the graph the box for students sitting in the back of the class is much bigger than those who are seated in middle or the front. This lets us understand that students who sit in the back of he classroom are more likely to consume alcohol.
    


## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
This graph shows how much people in each section drink, people in the front row drink 1.7 drinks on average. People in the middle row drink 3.3 drinks on average and people in the back row drink 8.5 drinks on average.People in the back drink more than both people who sit in the front or middle.
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
This graph shows a significant result, because the numbers are smaller than 0.05.

```{r}
plot(TukeyHSD(model1))
```

We can observe in the graph that there are differences in how much the people in the back are drinking and how much the people in middle and front are drinking. The people in the back are drinking much more than the people in the middle and front but the people in the middle and the front are not drinking more than each other.

## Conclusions


